Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-20 Manuscript/FLPhish(Trans).tex
修改bar plot样式

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[t]
  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Evaluated Scheme}
  \resizebox{0.5\textwidth}{!}{%
  \begin{tabular}{ll}
  \bottomrule
  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
  Ensemble FL                      & Ensemble Federated Learning                              \\ \hline
  FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline
  FLPhish($\tau=0.2$) & FLPhish-threshold with threshold $\tau=0.2$ \\ \hline
  FLPhish($\tau=0.5$) & FLPhish-threshold with threshold $\tau=0.5$ \\ \hline
  FLPhish(weight)                  & FLPhish-weight                                           \\ \hline
  \end{tabular}%
  }
  \end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[t]
  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Evaluated Scheme}
  \resizebox{0.5\textwidth}{!}{%
  \begin{tabular}{ll}
  \bottomrule
  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
  FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline
  FLPhish($\tau=0.2$) & FLPhish-threshold with threshold $\tau=0.2$ \\ \hline
  FLPhish($\tau=0.5$) & FLPhish-threshold with threshold $\tau=0.5$ \\ \hline
  FLPhish(weight)                  & FLPhish-weight                                           \\ \hline
  \end{tabular}%
  }
  \end{table}
